Management induced changes of soil organic carbon on global croplands

### 2020-12-11 SOCbudgetPaper/methods.Rmd
typo

To single out the impact of tillage practices, residue and manure inputs, we defined scenario with constant values for the three drivers: (1) In the \textit{constTillage} scenario the adoption of no-tillage practises are neglected (adoption starts in 1975 according to the available data set); (2) the \textit{constResidues} and the \textif{constManure} scenario assume constant input rates from residues resp. manure (in $\tfrac{t}{ha}$) at the level of 1975 onwards. Within the \textit{constResidue} scenario at least three effects overlay each other: (1) yields and with them residue biomass increase due to productivity gains, (2) rates of residue left or returned to fields are raising, and (3) shifts of crop groups change the amount of residue biomass due to crop-group specific harvest index values. The \textit{constManagement} combines all three scenarios.

>>>>

To single out the impact of tillage practices, residue and manure inputs, we defined scenario with constant values for the three drivers: (1) In the \textit{constTillage} scenario the adoption of no-tillage practices are neglected (adoption starts in 1974 according to the available data set); (2) the \textit{constResidues} and the \textif{constManure} scenario assume constant input rates from residues resp. manure (in $\tfrac{t}{ha}$) at the level of 1975 onwards. Within the \textit{constResidue} scenario at least three effects overlay each other: (1) yields and with them residue biomass increase due to productivity gains, (2) rates of residue left or returned to fields are raising, and (3) shifts of crop groups change the amount of residue biomass due to crop-group specific harvest index values. The \textit{constManagement} combines all three scenarios.
